Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-03 examples.tex
+

 \subsubsection{Ensuring Presence of an Entry}
After obtaining the identity mapping for \textsf{entry}, we are able to load the \textsf{entry\_val} into \textsf{rdi}, and check the presence bit via $and \;0x1,rdi$.
 Accessing the presence bit and checking the value allow (Lines 7-13 in Figure \ref{fig:calltopteinitialize}) us to exploit the fact in the side condition (*) in such a way that the condition ($\textsf{entry}\mapsto\textsf{present}$ determines whether we take the non-presence path (Lines 12-19 in Figure \ref{fig:calltopteinitialize}) with full ownership ($\textsf{qfrac} = 1$) to set the entry with proper values for the bitfields, e.g., frame showing freshly allocated page and presence bit.
 In case of absence, \textsf{pte\_initialize} is called for a physical-zeroed page (utilizing the page-allocator's \textsf{kalloc} -- currently the only axiom as it is not part of \textsf{pte} (virtual-memory-management) module) to be backing the physical frame address of the entry -- Specification Line 35 in Figure \ref{fig:calltopteinitialize}. Since we are using \textsf{pte\_initialize} for page-table address allocation, it also ensures us that newly allocated physicall address is in the identity mapping map $\Xi$ -- Line X in Figure \ref{fig:calltopteinitialize}.
\begin{figure}\footnotesize
  \begin{lstlisting}[mathescape]

>>>>

 \subsubsection{Ensuring Presence of an Entry}
After obtaining the identity mapping for \textsf{entry}, we are able to load the \textsf{entry\_val} into \textsf{rdi}, and check the presence bit via $and \;0x1,rdi$.
 Accessing the presence bit and checking the value (Line 19 in Figure \ref{fig:calltopteinitialize}) allow  us to exploit the fact in the side condition (*) in such a way that the condition ($\textsf{entry}\mapsto\textsf{present}$ determines whether we take the non-presence path (Lines 19-44 in Figure \ref{fig:calltopteinitialize}) with full ownership ($\textsf{qfrac} = 1$) to set the entry with proper values for the bitfields, e.g., frame showing freshly allocated page and presence bit.
 In case of absence, \textsf{pte\_initialize} is called for a physical-zeroed page (utilizing the page-allocator's \textsf{kalloc} -- currently the only axiom as it is not part of \textsf{pte} (virtual-memory-management) module) to be backing the physical frame address of the entry -- Specification Line 35 in Figure \ref{fig:calltopteinitialize}. Since we are using \textsf{pte\_initialize} for page-table address allocation, it also ensures us that newly allocated physicall address is in the identity mapping map $\Xi$ -- Line X in Figure \ref{fig:calltopteinitialize}.
\begin{figure}\footnotesize
  \begin{lstlisting}[mathescape]
